Simulated Observations of Young Gravitationally Unstable Protoplanetary Discs

### 2013-03-18 young_pp_discs.tex
minor text changes, sending round to authors second time in this form

Fig. \ref{continuum} shows the 1\,mm continuum emission and beam size in the chosen ALMA configuration. The spiral structure of the disc is clearly visible at this inclination and and it becomes clearer at angles closer to face-on. Integrating the flux from y=0.2 to -0.2 and x=0.4 to -0.4 and using the equation $M=frac{g S_\nu d^2}{\kappa_\nu B_\nu(T_d)}$ where g is the dust/gas mass ratio S$_\nu$ is the integrated flux, d is the distance to the source, $\kappa_\nu$ is the opacity and B$_\nu(T_d)$ is the black body function for a given dust temperature \citep{Beltran2006}. From this, a mass measurement of between 0.1$\,$M$_\odot$ and 0.005$\,$M$_\odot$ was obtained assuming temperatures of between 40-400K. This underestimates the disc mass by at least a factor of 4 and shows that in such young discs longer wavelength continuum observations may not be neccesary for determining the disc mass.\smallskip

>>>>

Fig. \ref{continuum} shows the 1\,mm continuum emission and beam size in the chosen ALMA configuration. The spiral structure of the disc is clearly visible at this inclination and and it becomes clearer at angles closer to face-on. Integrating the flux from y=0.2 to -0.2 and x=0.4 to -0.4 and using the equation $M=\frac{g S_\nu d^2}{\kappa_\nu B_\nu(T_d)}$ where g is the gas/dust mass ratio S$_\nu$ is the integrated flux, d is the distance to the source, $\kappa_\nu$ is the dust opacity and B$_\nu(T_d)$ is the black body function for a given dust temperature \citep{Beltran2006}. From this, a disc mass measurement of between 0.1$\,$M$_\odot$ and 0.005$\,$M$_\odot$ was obtained, assuming temperatures of between 40-400K, showing that the disc is not optically thin to millimetre wavelengths. This underestimate of the disc mass by at least a factor of 4 shows that in young, massive discs such as those we are investigating, longer wavelength continuum observations are neccesary for determining the disc mass.\smallskip
